\documentclass[12pt, letterpaper, twoside]{article}
\usepackage[utf8]{inputenc}

\title{Pepper Waiter HRI Project}
\author{Daniele Appetito Salvatore Cognetta Simone Rossetti}
        
\date{September 2021}

\begin{document}

\begin{titlepage}
\maketitle
\end{titlepage}

\tableofcontents
    
\newpage
\section{Introduction}

Human Robot Interaction is the study of how one or more humans work with one robots in order to accomplish a goal. The Pepper Waiter project was devised to create such an interaction. 

\

Pepper is a robot created by Softbank Robotics specifically to interact with people. It has tactile, visual, and audio sensors on its head to help a person convey  information in a variety of ways. On top of that it is equipped with an android tablet on its "chest" that can be used for further interaction. 

\

In this project we decided to create a program that allowed to use the Pepper in a bar or restaurant to take an order instead of a human. This idea came to us by thinking of the current global situation and how the less human-to-human contact there is, the better. As such we decided to create a way to adere to the social distancing norms by removing interaction with a human waiter. 

\


\




\section{Inspiration and Research}

For this projec

copy papers + parts of presentations ad justify them to the 

\section{Solution}

talk about what we decided to do to solve the proposed problem

\section{Implementation}

libraries and code desription

\section{Results}

mini description of functionality

\section{Conclusion}

Conclusion

\end{document}